---
title: "Report_Classification"
author: "Ethan"
date: "7-2-2021"
output: html_document
---

# - Set the Working Directory
```{r}
setwd("~/Desktop/Columbia Program Coding/project1.cl")
```

# - Load the libraries

The following are the required packages in order to run the project "project1.cl"

```{r warning=FALSE}
source("functions/libs.r")
libraries()
```

# - Import the Data

```{r warning=FALSE}
print("Importing the Data...")
source("scripts/import_data.R")
```

Above is the importation of the data, which is a time series containing `r colnames(data)`

# - Exploration of the Original

Looking at the original data, we noticed that all linear inputs 
`r c(colnames(data[,c(1:4)]))` demonstrates that all predictors reflect the same features.

```{r}
source("scripts/explore_O.r")
```

To confirm that the features reflect `r c(colnames(data[,c(1:4)]))`, we implemented a correlation analysis and noticed that all inputs are highly correlated.

```{r echo = F, fig.cap= 'Gridded Line Plots of the datasets'}
library(png)
library(grid)
img <- readPNG("./pictures/grid_line.png")
grid.raster(img)
```

```{r echo = F, fig.cap= 'Correlation Matrix of the datasets'}
library(png)
library(grid)
img <- readPNG("./pictures/cor_O.png")
grid.raster(img)
```

# - Preprocess the Data

In that case, we will removed the inputs `r c(colnames(data[,c(1:3, 6)]))` and prepared a new categrorical input to change the data from fitting a regression problem to a classification problem.

```{r}
source("scripts/prep.r")
```

After preprocessing the original data, our prep data contains the following variables: `r c(colnames(prep))`

# - Explore the Prep

```{r}
source("scripts/explore_P.r")
```

```{r echo = F, fig.cap= 'Gridded Line Plots of the Processed Datasets'}
img <- readPNG("./pictures/grid_line_P.png")
grid.raster(img)
```

```{r echo = F, fig.cap= 'Correlation Matrix Plot of the Processed Data'}
img <- readPNG("./pictures/cor_P.png")
grid.raster(img)
```

# - Classification Modeling

```{r message=FALSE, warning=FALSE}
source("modeling/modeling.r")
```

