---
title: 'Assignment #3 - Exploring the Data'
author: 'Ethan Wong'
date: "7/1/2021"
output: html_document
---

```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 

```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign3_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment3) for more direction.
Also, make sure to use the supporting scripts @ [06_explore_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/06_explore_data).

# Visualizations 

**Question #1:** Create a boxplot.

```{r}
#Importing the Data:
library(datasets)
data("iris")
data = iris 

#Importing the libraries necessary:
library(caret)
library(AppliedPredictiveModeling)

#Making the Box Plot:
featurePlot(x = data[, 1:4], 
            y = data$Species, 
            plot = "box", 
            ## Pass in options to bwplot() 
            scales = list(y = list(relation="free"),
                          x = list(rot = 90)),  
            layout = c(4,1 ), 
            auto.key = list(columns = 2))
```

**Question #2:** Create a barplot.

```{r}
#Importing the libraries:
library(ggplot2)

#Importing the Data:
data('iris')
data = iris 

#Creating the Bar plot:
p = ggplot(data, aes(Species, Sepal.Length)) +
  stat_summary(fun.y = mean,
               geom = "bar",
               fill = "White", 
               color = "Black") + 
  stat_summary(fun.data = mean_cl_normal, 
               geom = "errorbar", 
               position = position_dodge(width = 0.90), 
               width = 0.2) + 
  xlab('Iris Flower Type')+
  ylab('Measurements')
p
```

**Question #3:** Create a density plot.

```{r}
#The Libraries are already loaded, so now for the density plot
transparentTheme(trans = .9)
featurePlot(x = data[, 1:4], 
            y = data$Species,
            plot = "density", 
            ## Pass in options to xyplot() to 
            ## make it prettier
            scales = list(x = list(relation="free"), 
                          y = list(relation="free")), 
            adjust = 1.5, 
            pch = "|", 
            layout = c(4, 1), 
            auto.key = list(columns = 3))
```

**Question #4:** Create a lineplot. 

```{r}
#Libraries already loaded- straight to the line plot
#I didn't even realize that I made a pun until after reviewing this
p = ggplot(data, aes(Species, Sepal.Length)) +
  stat_summary(fun.y = mean, ##adds the points
               geom = "point") +
  stat_summary(fun.y = mean, ##adds the line
               geom = "line",
               aes(group=1)) +
  stat_summary(fun.data = mean_cl_normal, ##adds the error bars
               geom = "errorbar", 
               width = .2) +
  xlab('Iris Flower Type')+
  ylab('Measurement')
p
```

**Question #5:** create a historgram.

```{r}
#Libraries already loaded
p = ggplot(data, aes(Sepal.Width, color = Species)) + 
    geom_histogram(binwidth = 0.4) + 
    xlab("Iris Flower Type") + 
    ylab("Frequency")
p
```

**Question #6:** Create a scatterplot.

```{r}
p = ggplot(data, aes(Sepal.Width, Sepal.Length)) + 
  geom_point() +
  geom_smooth(method = 'lm', color = 'black') +
  xlab('Iris Flower Types')+
  ylab('Measurements')
p
```

**Question #7:** Create a scatterplot matrix. 

```{r}
#Importing Library GGally:
library(GGally)

#Graphing:
ggpairs(data, title = 'Sample Iris Data')
```

# Correlation 

**Question #8:** Create a Correlation Matrix.  

```{r}
#Libraries already all installed
cor = cor(data[,c(1:4)])
print(cor)
```

**Question #9:** Create a Correlation Matrix plot.

```{r}
#Importing Libraries
library(corrplot)
#Graphing (Using the Correlation matrix from above)
corrplot::corrplot(cor)
```

# Statistical Summaries 

**Question #10:** Create at least one statistical summary table as discussed in the course. 

```{r}
#I really liked how Hmisc works, so I'm gonna use that one
library(Hmisc)
Hmisc::describe(data)
```
