---
title: 'Assignment #1 - R and Python Learning'
author: 'Answer Key'
date: "4/12/2021"
output: html_document
---


```{r message=FALSE, warning=FALSE, include=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 
```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign1_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment1) for more direction.
Also, make sure to use the supporting scripts `py_learning.py` and `r_learning.r` @ [04_prepare.tools](https://github.com/jkorn81/cu-hsp-learning/tree/main/04_prepare.tools).


**Question #1:** Store the value 3 as `y` and the value 7 as `x`. 
Provide your response in R in the code chunk below. 

```{r}
y = 3
x = 7
print(c(x, y))
```

**Question #2:** Are you able to store and print the same variables in python?

```{python}
x = 7
y = 3
print([x, y])
```

**Question #3:** Store the x and y variables in a list and print it in R. 

```{r}
list = c(x, y)
print(list)
```

**Question #4:** Store the x and y variables in a list and print it in Python. 

```{python}
llist = [x, y]
print(llist)
```

**Question #5:** Index the $2^{nd}$ value in the list you stored in your R environment.

```{r}
list[2]
```

**Question #6:** Index the $2^{nd}$ value in the list you stored in your Python environment.

```{python}
llist[1]
```

**Question #7:** Create a square matrix containing the values $1,2,3,4$ in R. 

```{r}
x = c(1,3)
y = c(2,4)
matrix = as.matrix(cbind(x,y), ncol = 2, nrow = 2) 
print(matrix)
```

**Question #8:** Create a square matrix containing the values $1,2,3,4$ in Python. 

```{python}
import numpy as np
matrix = np.matrix('1 2 ; 3 4')
print(matrix)
```

**Question #9:** Create a dataframe in R with the column names of `x` and `y` containing $(1,2,3)$ and $(4,5,6)$.

```{r}
x = c(1,2,3)
y = c(4,5,6)
df = data.frame(x,y) 
colnames(df) = c("x", "y")
print(df)
```

**Question #10:** Create a function in Python to add $x+y$ and demonstrate it works by adding $3$ and $2$.

```{python}
def add(x,y):
  return x + y
add(3, 2)
```

**Question #11:** Create a loop that prints your name at least 10 times in R. 

```{r}
repetitions = 1
for (i in 1:10) {
  print('Ethan', str(repetitions))
  repetitions = repetitions + 1
}
```

**Question #12:** Import the dataset [hiccups.csv](https://github.com/jkorn81/cu-hsp-learning/blob/main/data/Hiccups.csv) in R and print a structure of the data. 


```{r}
library(readr)
setwd("~/Desktop/cu-hsp-learning-main") #Just throwing this in here because R was being stingy about the working directory even after setting it previously
text = read_csv("./data/Hiccups.csv")
str(text)
```

