---
title: 'Assignment #2 - Processing Data'
author: 'Ethan Wong'
date: "6/30/2021"
output: html_document
---

```{r echo=TRUE, message=FALSE, warning=FALSE}
options(width = 60)
library(reticulate) ### (... helps Rstudio connect to your python enviroment.)
py_config() # locate the direct path to your 
```

**Instructions** Provide your responses to the following questions in both R and Python. 
Follow the guidelines @  [assign2_guidelines](https://github.com/jkorn81/cu-hsp-learning/tree/main/assignments/assignment2) for more direction.
Also, make sure to use the supporting scripts @ [05_processing_data](https://github.com/jkorn81/cu-hsp-learning/tree/main/05_processing_data).

# Part 1 - Structured Data

**Question #1:** Import the iris csv from the course collection contained in `data` and print the structure of the dataframe using the `str()` function to show a representation of the object.

```{r echo=TRUE}
library(datasets)
library(readr)
setwd("~/Desktop/cu-hsp-learning-main/assignments/assignment2")
#Couldn't find it anywhere else, so I just found a path to an iris.csv with similar data

data = data.frame(read_csv('data/iris.csv'))
str(data)
```

**Question #2:** Subset any of the variables containing `Sepal` from the data. 

```{r echo=TRUE}
remove = c("sepal.width", 'sepal.length')
data = data[, !colnames(data) %in% c(remove)]
print(str(data))
#Not gonna use the subset_variable function just because we won't need to use it again.
#Obviously, in this case, I subsetted Sepal.Length from the data.
```

**Question #3:** Impute Missing/NA Values in the subsetted dataframe. 

```{r echo=TRUE}
#To make sure that we have all the packages that we need
if (!require("mice")) {
  install.packages("mice")
  library(mice)
}
if (!require("magrittr")) {
  library(magrittr)
}
#Wow! Surprisingly my mac can run this. Genuinely surprised.

missing = data %>% mice::mice(m=5,maxit=50,meth="sample",seed=500,print = FALSE)
missing <- mice::complete(missing, action=as.numeric(2))
data = na.omit(missing)
print(str(data))
```
*Question #4:** Convert the Variables in the dataframe as followed:

- `petal.width` and `petal.length` to numerical type. 
- `variety` to factor type. 

```{r echo=TRUE}
#They were already in numeric value, but just for practice:
data[, 'petal.width'] = as.numeric(data[, 'petal.width'])
data[, 'petal.width']

data[, 'petal.length'] = as.numeric(data[, 'petal.length'])
data[, 'petal.length']

#And now for converting to factor types:
data[, 'variety'] = as.factor(data[, 'variety'])
data[, 'variety']
```

**Question #5:** Normalize the Data, *(aka. Feature Engineering)* using `center, scale, and corr`.

```{r echo=TRUE}
if (!require('caret')) {
  install.packages("caret", dependencies = TRUE)
  library(caret)
}
#Not using corr because it ended up correlating the values of petal.length and petal.width maybe? Either way, it ended up omitting one of the data types so corr was deleted.
preProClean <- preProcess(x = data, method = c("scale", "center"))
data <- predict(preProClean, data %>% na.omit)
print(str(data))
```
**Bonus Question:** 

Does the last object have the variables in the correct data type? *(yes or no)*

```
#Yes, even though it isn't a numerical value, the factor data type is easiest to be read given the data within the variety datatype
```

# Part 2 - Unsturctured Text Data 

**Question #6:** Import the `text.csv` file from the course data collection. 

```{r echo=TRUE}
#Calling in library readr to make sure that it's here:
# Process Text ----
#install.packages('tm')
library(tm)
# install.packages('stringr')
library(stringr)

setwd("~/Desktop/cu-hsp-learning-main/assignments/assignment2")
#Forcing the Program to recognize this as the working directory

data <- data.frame(read.csv("./data/text.csv"))
data = tail(data,100)
colnames(data) = c('text','class')
str(data)
```

**Question #7:** Process the text data and class as reflected in the code contained in file `preprocess_text.r` from lines $10 - 23$. 

```{r echo=TRUE}
#Starting at line 11 of preprocess_text.r since we already previewed the unedited text before:
text = c(lapply(data$text, as.character)) # convert to string/character format...
data.text = text
data.text = tolower(data.text) # convert letter casing to lower...
data.text = tm::removeWords(data.text, stopwords("SMART")) # remove words like t(the, a, an, etc...)
data.text = iconv(data.text, "latin1", "ASCII", sub = " ") # remove special characters...
data.text = gsub("^NA| NA ", " ", data.text) # remove all NA values/patterns...
data.text = tm::removePunctuation(data.text) # remove punctuation...
data.text = tm::removeNumbers(data.text) # remove numbers...
data.text = tm::stripWhitespace(data.text) # remove whitespace... 

#Leaving the comments in from preprocess_text.r so that we know what each command does,

# merge text w/ labels again...
merged.data = data.frame(cbind(data.text, data$class))
colnames(merged.data) = c("text", "class")
merged.data$text = as.character(merged.data$text)
str(merged.data)
```

# Part 3 - Unstructured Image Data

**Question #8:** Locate some images representing two states from the internet *(i.e. sunny skies, cloudy skies)* and sort them into `train and validation` folder scheme and import them as shown in the script `image_processing.r`. Make sure to print back your the number of samples in each folder that you imported.  

```{r echo=TRUE}
# - Packages...
library(keras)
library(tensorflow)
library(reticulate)
library(tfruns)
library(viridis) 

# - [1] - Model 1===================================================
start <- Sys.time()
image_list <- c("0", "1") 

# number of output classes (i.e. Classes (0 & 1))
output_n <- length(image_list)

# image size to scale down to (original images are 50 x 50 px)
img_width <- 50
img_height <- 50
target_size <- c(img_width, img_height)

# RGB = 3 channels
channels <- 3

# path to image folders
#Using a new folder for this, named image. This folder just contains some photos of the moon and photos of the night sky without the moon.
#If needed, I could also post that folder to canvas.
path.train = "data/image/train"
train_image_files_path <- file.path(path.train)
path.valid = "data/image/valid"
valid_image_files_path <- file.path(path.valid)

# optional data augmentation
train_data_gen = image_data_generator(
  rescale = 1/255,
  featurewise_center = T,
  featurewise_std_normalization = T,
  samplewise_std_normalization = T,
  rotation_range = 2,
  shear_range=0.2,
  zoom_range=0.2,
  horizontal_flip=TRUE,
  vertical_flip = TRUE,
  zca_whitening = TRUE,
  validation_split = 0.2
  #augment = TRUE
)

# Validation data shouldn't be augmented! But it should also be scaled.
valid_data_gen <- image_data_generator(
  rescale = 1/255,
  validation_split = 0.2
)  

#Adding in this just because the program kept on getting confused and changing the directory that I wanted to go to, so I just forced the program to look here for this cell.
setwd("~/Desktop/cu-hsp-learning-main")

# training images
train_image_array_gen <- flow_images_from_directory(train_image_files_path, 
                                                    generator =train_data_gen,
                                                    target_size = target_size,
                                                    color_mode = "rgb",
                                                    class_mode = 'categorical',
                                                    shuffle=TRUE,
                                                    #Shuffling to make sure that it's                                                     not mistaken as a pattern
                                                    classes = image_list,
                                                    subset = 'training',
                                                    #interpolation = "bilinear",
                                                    seed = 42)

# validation images
valid_image_array_gen <- flow_images_from_directory(valid_image_files_path, 
                                                    generator = valid_data_gen,
                                                    target_size = target_size,
                                                    color_mode = "rgb",
                                                    class_mode = 'categorical',
                                                    shuffle=TRUE,
                                                    classes = image_list,
                                                    subset = 'validation',
                                                    #interpolation = "bilinear",
                                                    seed = 42)


test_image_array_gen <- flow_images_from_directory(valid_image_files_path, 
                                                   generator = valid_data_gen,
                                                   target_size = target_size,
                                                   color_mode = "rgb",
                                                   class_mode = 'categorical',
                                                   shuffle=TRUE,
                                                   classes = image_list,
                                                   subset = 'validation',
                                                   #interpolation = "bilinear",
                                                   seed = 42)

### model definition

# number of training samples
train_samples <- train_image_array_gen$n
train_samples

# number of validation samples
valid_samples <- valid_image_array_gen$n
valid_samples
```